One-dimensional Classical Gas in a Harmonic Trap with Repulsive Interaction

### 2017-01-19 Zhiyu.tex
Jan19 PRE format, tex

One the other hand, in a nonquilibrium many-body system, a more intriguing question is about its thermalization or relaxation property. Thermalization is among the most fundamental process for a many-body interacting system. All systems do not thermalize. An example is the Fermi-Pasta-Ulam paradox [ ] which shows confinement in phase-space so that the system stay non-thermalized for a long time. A lot of research on thermalization property has been done in other classical system. Ref.\cite{Tsuchiya2000}\cite{Yawn1997} studied the one dimensional gravitational system with Lyapunov exponents. Ref.\cite{Jin2013} studied the ring of harmonic oscillators and magnetic moment by examine the canonical distribution of a subsystem . In our paper, we will also probe the system's thermalization time scales from the perspective of canonical distribution as wel as Lyapunov exponent. Wiht these approaches, we will show that the thermalization time scale manifest a competition between total energy and interaction energy, so there is not any singular behaviour in the thermalization time scales except the trivial divergence at zero interaction.

This paper is organized as follows: In Section \ref{section:preparation}, we perform a scaling to reduce the parameter of the system. In addition, we briefly observe the ground state and reveal two dynamically distinct regime of the system, i.e. strong interaction regime and weak interaction regime. In Section \ref{section:breathing frequency}, we evaluate the breathing frequency according to its mechanism, and compare that with our numerical simulation result. Besides, we also introduce a rotating frame method of treating this problem, which is a convenient tool to analyze simple harmonic systems. In section \ref{section:Thermalization}, we focus on the thermalization property. We first examine the canonical disribution of energy to find out the threshold of thermalization, i.e. under what parameter the thermalization time scale is very large. Then we point out that there are two kind of thermalization (or relaxation) behaviour that could be measured in this system. In the end of this section, we measure the Lyapunov Exponent to quantify the time scales and confirm the former discussion.

@@

\subsubsection{Ground states}
For the ground state of this system, one could predict that \\(1) When the $\sigma$ is larger than the size of the cloud (in view of the scaling behaviour, large $\sigma$ is equivalent to small $F_0$ limit when we fix $\sigma=1$), it can be easily shown that the ground state is crystal-like, since all every particle keeps an equal distance with its nearest neighbours, which is $\frac{2F_0}{\omega_0^2}$. The low-lying excitation is particles' independent harmonic oscillation around their equilibrium position.\\(2) When $F_0$ is very large the molecules act like a hardcore gas, while the size of particle is just $\sigma$.

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_GS_pre_2_rev.eps}
\caption{particles' position at ground states }
\label{fig:GS1}
\end{figure}

@@

\section{Breathing Frequency}\label{section:breathing frequency}
Usually, to see the response of quantum gas to a quench, one begin simulation with the ground state and then suddenly vary some parameter by a little, for instance, $\omega_0'\rightarrow\omega_0=\omega_0'+\Delta\omega$. In that case, one will observe the radius R oscillating at a certain frequency, which is usually called ``breathing mode".
However, it is quite different in the classical version. Firstly, the ground state may be meaningless. In quantum case, the reason why we care about ground state and low lying excitations is that BEC occur at low temperature. But in classical case, there is no BEC. So it is not necessary to focus on low lying excitations in classical case. Besides, since classical limit is $\bar{h}\rightarrow 0$, no matter how low the kT is, $\bar{h}/kT$ is always zero so that classical behavious of low lying excitations is quite different from the quantum one. Secondly, it is no longer necessary to vary parameters ``by a little" in the quench. In quantum case, the small quench $\omega_0'\rightarrow\omega_0=\omega_0'+\Delta\omega$ means the spectrum is shifted slightly, thus one may expect to see some beat phenomenon({\color{red}{?}}). But in classical case, since $\bar{h}$ vanishes, no matter how small the quench is, one can never recover or proximate the quantum case. Thus it is not necessary to limit ourselves to small quench.

@@

Since the number of particles we use in the Molecular Dynamics simulation is limited (usually 5 to 20), the random noise is significant. If we start with a state whose configuration in phase-space is an ellipse slightly deviated from circle, the oscillating amplitude will be too small to be distinguished from noise. Therefore, we start from an extreme case -- line distribution (random x, zero p) and observe the oscillation of R(t). 
\begin{figure}[hbtp]
\center
\includegraphics[scale=0.32]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanF_differentE_log_2_with_oscillation_demo.png}
\caption{breathing mode frequency measured at different E and $F_0$. Insert: a demonstration of oscillation, $E_{trap}$ is the total potential energy of particles in the trap, which is proportional to $\sum_{is}{x_i^2}$, thus manifest the oscillation behaviour of radius R(t) defined in Eq.\ref{eq:def_of_R}. The breathing frequency is measured by taking Fourier transformation of R(t).}
\label{fig:Breathingfrequency1}
\end{figure}

Without interaction, the breathing mode frequency is exactly 2. When there is interaction, the frequency will drift to some other value near 2. We measure the radius of the cloud $R(t)$ and get the frequency spectrum of its oscillation behaviour by Fourier transform. Then we take the peak frequency near 2 as the breathing mode frequency. The frequency measured in different E and $F_0$ is shown in the Fig.\ref{fig:Breathingfrequency1}.

@@

\begin{figure*}
\subfigure[$t=0$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.21]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=1-5T_rev.eps} 
\includegraphics[scale=0.22]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=1-5T_rev.eps}
\end{minipage}
}
\subfigure[$t=\frac{1}{5}T$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.21]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=2-5T_rev.eps} 
\includegraphics[scale=0.22]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=2-5T_rev.eps}
\end{minipage}
}\subfigure[$t=\frac{2}{5}T$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.21]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=3-5T_rev.eps} 
\includegraphics[scale=0.22]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=3-5T_rev.eps}
\end{minipage}
}\subfigure[$t=\frac{3}{5}T$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.21]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=4-5T_rev.eps} 
\includegraphics[scale=0.22]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=4-5T_rev.eps}
\end{minipage}
}\subfigure[$t=\frac{4}{5}T$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.21]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=5-5T_rev.eps} 
\includegraphics[scale=0.22]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=5-5T_rev.eps}
\end{minipage}
}
\caption{N=50,F0=100,E=50000. Upper(lower) five pictures are snapshot of the configuration of the cloud in the stationary(rotating) frame at t=$\frac{1}{5}T$, $\frac{2}{5}T$, $\frac{3}{5}T$, $\frac{4}{5}T$, $T$ respectively.}
\end{figure*}

\begin{figure*}
\includegraphics[scale=0.23]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=0T_rev.eps} 
\includegraphics[scale=0.23]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=20T_rev.eps}
\includegraphics[scale=0.23]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=40T_rev.eps} 
\includegraphics[scale=0.23]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=60T_rev.eps}
\includegraphics[scale=0.23]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=80T_rev.eps} 
\caption{the precession behaviour of cloud viewed in the rotating frame in phase-space. $\frac{t}{T}=0,20,40,60,80$}
\label{fig:Breathingfrequency2_1}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/bounce.png}
\includegraphics[scale=0.32]{D:/matlab2016/MolecularDynamics/figure/latexpic/pass.png}
\caption{a schematic diagram of the collision process: \textbf{(a)}(Upper)when $F_0*\sigma$ is big, particles can not penetrate each other, thus their trajectory in rotating frame is a circular arc.  \textbf{(b)} (Lower) When $F_0*\sigma$ is small, particles easily pass each other, so that the force they feel is not continuous, their trajectory has a turning point(the dashed bright blue trajectory is identical with the one in the upper figure, which is the critical situation between passing and bouncing, that is to say, particles have zero relative velocity when they collide.) }
\label{fig:Breathingfrequency3}
\end{figure}

@@

When $F_0$ is not that large, the frequency behaviour seems complicated (see fig.\ref{fig:Breathingfrequency1}). Usually, when $F_0$ increase, frequency goes down below 2 first and then rise up and converge to some value higher than 2. The reason could also be well understood with the mechanism described before. In the former discussion, we goes to high $F_0$ limit, which means particles exchange momentum in infinitesimal time. For $F_0$ is not very big, the finite interaction time should be taken into consideration. During this time, the behaviour of each particle in phase space is exactly moving along the direction of the real P axis at 'velocity' $F0/m$. Since the real P axis is rotating counter-clockwise, the particle will follow the circular trajectory(orange and green dashed line in fig.\ref{fig:Breathingfrequency3}) the $\alpha$ that we once use to estimate the precession motion should decrease with the increase of interaction time. There should be some ``critical point" where $\alpha$ goes from plus to minus (dashed green line). At this point, we will see the precession stop so that the frequency is 2.

\begin{figure}
\centering
\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanF_scanE_pre.eps}
\caption{dependence of breathing frequency on Energy, N=20. Different color stands for different $F_0$: {\color{red}{Red}} for $F_0$=2000; {\color{yellow}{Yellow}} for $F_0$=3000; {\color{green}{Green}} for $F_0$=10000;  {\color{blue}{Blue}} for $F_0$=100000. Run with 3 different initial states in each case, and in each run, measure the frequency in 0-100 time unit(label as crosses) and in 900-1000 time unit (label as circles). The black dashed line is the prediction of Eq.\ref{eq:breathingfrequency1}.}
\label{fig:Breathingfrequency4}
\end{figure}

The dependence of frequency on energy and $F_0$ is shown in fig.\ref{fig:Breathingfrequency4}. For the first thing, as expected when $F_0$ is high the frequency behaviour is well-described by linear prediction Eq.\ref{eq:breathingfrequency1}. Secondly, the figure shows the frequency's dependence on $F_0$. As we explained, when $F_0$ is not so large, the precession angle decrease. In language of real space, the finite $F_0$ create a finite approaching time, thus consumes the time saved by finite-range collision. As a result, the frequency should be lower when $F_0$ decrease, and reach 2 earlier.

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/effective_potential.png}
\caption{effective potential for two-particle system}
\label{fig:thermalization2}
\end{figure}

@@

\subfigure[$E_i=2$]{
\begin{minipage}[b]{0.22\textwidth}
\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_23_N=2_F0=1_Er=2_single_particle_energy_pre.eps} 
%\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=2_phasespace.eps}
\end{minipage}
}
\subfigure[$E_i=3$]{
\begin{minipage}[b]{0.22\textwidth}
\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_23_N=2_F0=1_Er=3_single_particle_energy_pre.eps} 
%\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=3_phasespace.eps}
\end{minipage}
}
\subfigure[$E_i=5$]{
\begin{minipage}[b]{0.22\textwidth}
\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_23_N=2_F0=1_Er=5_single_particle_energy_pre.eps} 
%\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=5_phasespace.eps}
\end{minipage}
}
\subfigure[$E_i=10$]{
\begin{minipage}[b]{0.22\textwidth}
\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_23_N=2_F0=1_Er=10_single_particle_energy_pre.eps} 
%\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=10_phasespace.eps}
\end{minipage}
}

@@

\subsubsection{More particles}
Now let's consider the three-particle case. For two particle, the motion is non-chaotic. On the other hand, intuitively, we will say that three-body motion is chaotic so that the system could be ``thermalized" soon. However, in some cases, the time scale of thermalizing could still be very long. Suppose two of them, say, A and B, has small internal energy, which means their distance and relative velocity are both small. Meanwhile, suppose particle C has some energy quite different from A \& B. In this case, A \& B will often be in the interaction, while C will pass both of them at a high speed in each period. How will energy transfer between C and the two-particle system A and B? Since the relative velocity of C and the two-particle system is usually large, C will pass A-B pair in a short time $\tau\sim\frac{\sigma}{R}$ ($\tau\ll\frac{2\pi}{\omega}$). C gives A a push when approaching it, and then push A back when leaving.  As has been discussed in the two-particle case, this process is equivalent to giving A a very small speed($\sim O(\frac{\sigma}{R})$) in the background of a trap. Since both the position and velocity of A and B are close($|x_A-x_B|\sim\sigma$), the velocity increase of A \& B are almost the same (difference$\sim O(\frac{\sigma^2}{R^2})$). In this manner, the passing of particle C only kicks the center of mass of the A-B pair slightly, leaving the internal motion of the pair unaffected. In another word, the existence of C will not have significant effect on the energy transfer between A and B, but only ``dance" with their center of mass. The physics of the ``dance" is similar to the dance between two particle. As is shown in fig.\ref{fig:thermalization4}, the particles with energy close to each other tends to form a pair with small internal energy and the pair's internal energy transfer is relatively stable.

\begin{figure}
\centering
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/pair1_pre.eps}
\caption{evolution of single-particle energy}
\label{fig:thermalization4}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
%\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution1_scanF0_E=100_3.eps}
%\caption{Distribution scan $F_0$, $E=100$, $N=5$, $\sigma=1$ {\color{red}{Run again!}} }
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_energydistribution_pre_rev.eps} 
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=10_energydistribution_pre_rev.eps} 
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_energydistribution_pre_rev.eps}
\caption{the energy distribution measured in $\sim 10000$ time units, as will be verified later, {\color{green}{green}} curves corresponds to Boltzmann distribution; {\color{red}{red}} curves are obviously non-Boltzmann, while the {\color{yellow}{yellow}} ones are intermediate case, represent ``thermalization threshold". In three figures for different N, we choose E/N identical (=1000), and thermalization is reached at $F_0=500$-$F_0=1000$, which is consistent with our prediction in Eq.\ref{eq:thermalizatiton condition}}
\label{fig:thermalization5}

@@

\begin{figure}
\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_23_N=10_single_particle_energy_F0=200_pre.eps} 
\caption{energy of each particle, $F_0=200$}
\label{fig:thermalization6}

\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_23_N=10_single_particle_energy_F0=1000_pre.eps} 
\caption{energy of each particle, $F_0=1000$}
\label{fig:thermalization7}
\end{figure}

@@

One may think that this condition only means that the energy transfer in every collision is much smaller than the energy interval. But this is not the whole story. The essential difference between these two regime lies in whether the energy transfer in every collision is correlated: In thermalizable regime, the energy transfer in every collision is much smaller than the energy interval, which definitly slows down the energy transfer. What is more, because of this, the particles is less interfered by other particles so that two-particle analysis survives. It means that for a particle pair, the energy transferred in this collision is correlated with the one in the next time. In this manner, each particle in the pair will pick up some energy in several collisions, and then return it back to its partner -- which is just what the long term beat effect tells us. Thus the particles energy is localized in certain value. On the contrary, if we go to non-thermalizable regime, the energy transfer is so fast that for each particle don't remember their partners. As a result, the energy transferred in every collision between two particles are no longer correlated, which is equivalent to say that two-particle analysis breaks down. Instead, the energy transfer is completely random, with a non-zero amplitude. On the single-particle energy diagram, what we expected to see is a ``one dimensional random walk" ,so energy levels quickly spread around the diagram.

@@

But intuitively, one will expect that if we measure the energy of a subsystem , e.g. one particle, then we will get a Boltzmann distribution because the rest part of the system serves as a bath for this particle. The temperature of this isolated system is defined according to $Nk_BT=E$. It is evident that this argument only hold when the energy of the single particle is not too big --- if one particle take up 50\% of the total energy, the rest could no longer be thought of as a good bath.

>>>>

One the other hand, in a nonquilibrium many-body system, a more intriguing question is about its thermalization or relaxation property. Thermalization is among the most fundamental process for a many-body interacting system. All systems do not thermalize. An example is the Fermi-Pasta-Ulam paradox [ ] which shows confinement in phase-space so that the system stay non-thermalized for a long time. A lot of research on thermalization property has been done in other classical system. Ref.\cite{Tsuchiya2000}\cite{Yawn1997} studied the one dimensional gravitational system with Lyapunov exponents. Ref.\cite{Jin2013} studied the ring of harmonic oscillators and magnetic moment by examine the canonical distribution of a subsystem . In our paper, we will also probe the system's thermalization time scales from the perspective of canonical distribution as well as Lyapunov exponent. With these approaches, we will show that the thermalization time scale manifest a competition between total energy and interaction energy, so there is not any singular behavior in the thermalization time scales except the trivial divergence at zero interaction.

This paper is organized as follows: In Section \ref{section:preparation}, we perform a scaling to reduce the parameter of the system. In addition, we briefly observe the ground state and reveal two dynamically distinct regime of the system, i.e. strong interaction regime and weak interaction regime. In Section \ref{section:breathing frequency}, we evaluate the breathing frequency according to its mechanism, and compare that with our numerical simulation result. Besides, we also introduce a rotating frame method of treating this problem, which is a convenient tool to analyze simple harmonic systems. In section \ref{section:Thermalization}, we focus on the thermalization property. We first examine the canonical distribution of energy to find out the threshold of thermalization, i.e. under what parameter the thermalization time scale is very large. Then we point out that there are two kind of thermalization (or relaxation) behavior that could be measured in this system. In the end of this section, we measure the Lyapunov Exponent to quantify the time scales and confirm the former discussion.

@@

\subsubsection{Ground states}
For the ground state of this system, one could predict that \\(1) When the $\sigma$ is larger than the size of the cloud (in view of the scaling behavior, large $\sigma$ is equivalent to small $F_0$ limit when we fix $\sigma=1$), it can be easily shown that the ground state is crystal-like, since all every particle keeps an equal distance with its nearest neighbors, which is $\frac{2F_0}{\omega_0^2}$. The low-lying excitation is particles' independent harmonic oscillation around their equilibrium position.\\(2) When $F_0$ is very large the molecules act like a hardcore gas, while the size of particle is just $\sigma$.

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.6]{ZhiyuPictures/N=5_GS_pre_2_rev.eps}
\caption{particles' position at ground states }
\label{fig:GS1}
\end{figure}

@@

\section{Breathing Frequency}\label{section:breathing frequency}
Usually, to see the response of quantum gas to a quench, one begin simulation with the ground state and then suddenly vary some parameter by a little, for instance, $\omega_0'\rightarrow\omega_0=\omega_0'+\Delta\omega$. In that case, one will observe the radius R oscillating at a certain frequency, which is usually called ``breathing mode".
However, it is quite different in the classical version. Firstly, the ground state may be meaningless. In quantum case, the reason why we care about ground state and low lying excitations is that BEC occur at low temperature. But in classical case, there is no BEC. So it is not necessary to focus on low lying excitations in classical case. Besides, since classical limit is $\hbar\rightarrow 0$, no matter how low the kT is, $\hbar/kT$ is always zero so that classical behavious of low lying excitations is quite different from the quantum one. Secondly, it is no longer necessary to vary parameters ``by a little" in the quench. In quantum case, the small quench $\omega_0'\rightarrow\omega_0=\omega_0'+\Delta\omega$ means the spectrum is shifted slightly, thus one may expect to see some beat phenomenon({\color{red}{?}}). But in classical case, since $\hbar$ vanishes, no matter how small the quench is, one can never recover or proximate the quantum case. Thus it is not necessary to limit ourselves to small quench.

@@

Since the number of particles we use in the Molecular Dynamics simulation is limited (usually 5 to 20), the random noise is significant. If we start with a state whose configuration in phase-space is an ellipse slightly deviated from circle, the oscillating amplitude will be too small to be distinguished from noise. Therefore, we start from an extreme case -- line distribution (random x, zero p) and observe the oscillation of R(t). 
\begin{figure}[hbtp]
\center
\includegraphics[scale=0.32]{ZhiyuPictures/freq_scanF_differentE_log_2_with_oscillation_demo.png}
\caption{breathing mode frequency measured at different E and $F_0$. Insert: a demonstration of oscillation, $E_{trap}$ is the total potential energy of particles in the trap, which is proportional to $\sum_{is}{x_i^2}$, thus manifest the oscillation behavior of radius R(t) defined in Eq.\ref{eq:def_of_R}. The breathing frequency is measured by taking Fourier transformation of R(t).}
\label{fig:Breathingfrequency1}
\end{figure}

Without interaction, the breathing mode frequency is exactly 2. When there is interaction, the frequency will drift to some other value near 2. We measure the radius of the cloud $R(t)$ and get the frequency spectrum of its oscillation behavior by Fourier transform. Then we take the peak frequency near 2 as the breathing mode frequency. The frequency measured in different E and $F_0$ is shown in the Fig.\ref{fig:Breathingfrequency1}.

@@

\begin{figure*}
\subfigure[$t=0$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=1-5T_rev.eps} 
\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=1-5T_rev.eps}
\end{minipage}
}
\subfigure[$t=\frac{1}{5}T$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=2-5T_rev.eps} 
\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=2-5T_rev.eps}
\end{minipage}
}\subfigure[$t=\frac{2}{5}T$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=3-5T_rev.eps} 
\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=3-5T_rev.eps}
\end{minipage}
}\subfigure[$t=\frac{3}{5}T$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=4-5T_rev.eps} 
\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=4-5T_rev.eps}
\end{minipage}
}\subfigure[$t=\frac{4}{5}T$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=5-5T_rev.eps} 
\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=5-5T_rev.eps}
\end{minipage}
}
\caption{N=50,F0=100,E=50000. Upper(lower) five pictures are snapshot of the configuration of the cloud in the stationary(rotating) frame at t=$\frac{1}{5}T$, $\frac{2}{5}T$, $\frac{3}{5}T$, $\frac{4}{5}T$, $T$ respectively.}
\end{figure*}

\begin{figure*}
\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=0T_rev.eps} 
\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=20T_rev.eps}
\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=40T_rev.eps} 
\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=60T_rev.eps}
\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=80T_rev.eps} 
\caption{the precession behavior of cloud viewed in the rotating frame in phase-space. $\frac{t}{T}=0,20,40,60,80$}
\label{fig:Breathingfrequency2_1}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[scale=0.3]{ZhiyuPictures/bounce.png}
\includegraphics[scale=0.32]{ZhiyuPictures/pass.png}
\caption{a schematic diagram of the collision process: \textbf{(a)}(Upper)when $F_0*\sigma$ is big, particles can not penetrate each other, thus their trajectory in rotating frame is a circular arc.  \textbf{(b)} (Lower) When $F_0*\sigma$ is small, particles easily pass each other, so that the force they feel is not continuous, their trajectory has a turning point(the dashed bright blue trajectory is identical with the one in the upper figure, which is the critical situation between passing and bouncing, that is to say, particles have zero relative velocity when they collide.) }
\label{fig:Breathingfrequency3}
\end{figure}

@@

When $F_0$ is not that large, the frequency behavior seems complicated (see fig.\ref{fig:Breathingfrequency1}). Usually, when $F_0$ increase, frequency goes down below 2 first and then rise up and converge to some value higher than 2. The reason could also be well understood with the mechanism described before. In the former discussion, we goes to high $F_0$ limit, which means particles exchange momentum in infinitesimal time. For $F_0$ is not very big, the finite interaction time should be taken into consideration. During this time, the behavior of each particle in phase space is exactly moving along the direction of the real P axis at 'velocity' $F0/m$. Since the real P axis is rotating counter-clockwise, the particle will follow the circular trajectory(orange and green dashed line in fig.\ref{fig:Breathingfrequency3}) the $\alpha$ that we once use to estimate the precession motion should decrease with the increase of interaction time. There should be some ``critical point" where $\alpha$ goes from plus to minus (dashed green line). At this point, we will see the precession stop so that the frequency is 2.

\begin{figure}
\centering
\includegraphics[scale=0.6]{ZhiyuPictures/freq_scanF_scanE_pre.eps}
\caption{dependence of breathing frequency on Energy, N=20. Different color stands for different $F_0$: {\color{red}{Red}} for $F_0$=2000; {\color{yellow}{Yellow}} for $F_0$=3000; {\color{green}{Green}} for $F_0$=10000;  {\color{blue}{Blue}} for $F_0$=100000. Run with 3 different initial states in each case, and in each run, measure the frequency in 0-100 time unit(label as crosses) and in 900-1000 time unit (label as circles). The black dashed line is the prediction of Eq.\ref{eq:breathingfrequency1}.}
\label{fig:Breathingfrequency4}
\end{figure}

The dependence of frequency on energy and $F_0$ is shown in fig.\ref{fig:Breathingfrequency4}. For the first thing, as expected when $F_0$ is high the frequency behavior is well-described by linear prediction Eq.\ref{eq:breathingfrequency1}. Secondly, the figure shows the frequency's dependence on $F_0$. As we explained, when $F_0$ is not so large, the precession angle decrease. In language of real space, the finite $F_0$ create a finite approaching time, thus consumes the time saved by finite-range collision. As a result, the frequency should be lower when $F_0$ decrease, and reach 2 earlier.

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.2]{ZhiyuPictures/effective_potential.png}
\caption{effective potential for two-particle system}
\label{fig:thermalization2}
\end{figure}

@@

\subfigure[$E_i=2$]{
\begin{minipage}[b]{0.22\textwidth}
\includegraphics[scale=0.3]{ZhiyuPictures/10_23_N=2_F0=1_Er=2_single_particle_energy_pre.eps} 
%\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=2_phasespace.eps}
\end{minipage}
}
\subfigure[$E_i=3$]{
\begin{minipage}[b]{0.22\textwidth}
\includegraphics[scale=0.3]{ZhiyuPictures/10_23_N=2_F0=1_Er=3_single_particle_energy_pre.eps} 
%\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=3_phasespace.eps}
\end{minipage}
}
\subfigure[$E_i=5$]{
\begin{minipage}[b]{0.22\textwidth}
\includegraphics[scale=0.3]{ZhiyuPictures/10_23_N=2_F0=1_Er=5_single_particle_energy_pre.eps} 
%\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=5_phasespace.eps}
\end{minipage}
}
\subfigure[$E_i=10$]{
\begin{minipage}[b]{0.22\textwidth}
\includegraphics[scale=0.3]{ZhiyuPictures/10_23_N=2_F0=1_Er=10_single_particle_energy_pre.eps} 
%\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=10_phasespace.eps}
\end{minipage}
}

@@

\subsubsection{More particles}
Now let's consider the three-particle case. For two particle, the motion is non-chaotic. On the other hand, intuitively, we will say that three-body motion is chaotic so that the system could be ``thermalized" soon. However, in some cases, the time scale of thermalizing could still be very long. Suppose two of them, say, A and B, has small internal energy, which means their distance and relative velocity are both small. Meanwhile, suppose particle C has some energy quite different from A \& B. In this case, A \& B will often be in the interaction, while C will pass both of them at a high speed in each period. How will energy transfer between C and the two-particle system A and B? Since the relative velocity of C and the two-particle system is usually large, C will pass A-B pair in a short time $\tau\sim\frac{\sigma}{R}$ ($\tau\ll\frac{2\pi}{\omega}$). C gives A a push when approaching it, and then push A back when leaving.  As has been discussed in the two-particle case, this process is equivalent to giving A a very small velocity ($\sim O(\frac{\sigma}{R})$) in the background of a trap. Since both the position and velocity of A and B are close($|x_A-x_B|\sim\sigma$), the velocity increase of A \& B are almost the same (difference$\sim O(\frac{\sigma^2}{R^2})$). In this manner, the passing of particle C only kicks the center of mass of the A-B pair slightly, leaving the internal motion of the pair unaffected. In another word, the existence of C will not have significant effect on the energy transfer between A and B, but only ``dance" with their center of mass. The physics of the ``dance" is similar to the dance between two particle. As is shown in fig.\ref{fig:thermalization4}, the particles with energy close to each other tends to form a pair with small internal energy and the pair's internal energy transfer is relatively stable.

\begin{figure}
\centering
\includegraphics[scale=0.5]{ZhiyuPictures/pair1_pre.eps}
\caption{evolution of single-particle energy}
\label{fig:thermalization4}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
%\includegraphics[scale=0.2]{ZhiyuPictures/distribution1_scanF0_E=100_3.eps}
%\caption{Distribution scan $F_0$, $E=100$, $N=5$, $\sigma=1$ {\color{red}{Run again!}} }
\includegraphics[scale=0.5]{ZhiyuPictures/N=5_energydistribution_pre_rev1.eps} 
\includegraphics[scale=0.5]{ZhiyuPictures/N=10_energydistribution_pre_rev1.eps}
\includegraphics[scale=0.5]{ZhiyuPictures/N=20_energydistribution_pre_rev1.eps}
\caption{the energy distribution measured in $\sim 10000$ time units, as will be verified later, {\color{green}{green}} curves corresponds to Boltzmann distribution; {\color{red}{red}} curves are obviously non-Boltzmann, while the {\color{yellow}{yellow}} ones are intermediate case, represent ``thermalization threshold". In three figures for different N, we choose E/N identical (=1000), and thermalization is reached at $F_0=500$-$F_0=1000$, which is consistent with our prediction in Eq.\ref{eq:thermalizatiton condition}}
\label{fig:thermalization5}

@@

\begin{figure}
\includegraphics[scale=0.6]{ZhiyuPictures/10_23_N=10_single_particle_energy_F0=200_pre.eps} 
\caption{energy of each particle, $F_0=200$}
\label{fig:thermalization6}

\includegraphics[scale=0.6]{ZhiyuPictures/10_23_N=10_single_particle_energy_F0=1000_pre.eps} 
\caption{energy of each particle, $F_0=1000$}
\label{fig:thermalization7}
\end{figure}

@@

One may think that this condition only means that the energy transfer in every collision is much smaller than the energy interval. But this is not the whole story. The essential difference between these two regime lies in whether the energy transfer in every collision is correlated: In thermalizable regime, the energy transfer in every collision is much smaller than the energy interval, which definitely slows down the energy transfer. What is more, because of this, the particles is less interfered by other particles so that two-particle analysis survives. It means that for a particle pair, the energy transferred in this collision is correlated with the one in the next time. In this manner, each particle in the pair will pick up some energy in several collisions, and then return it back to its partner -- which is just what the long term beat effect tells us. Thus the particles energy is localized in certain value. On the contrary, if we go to non-thermalizable regime, the energy transfer is so fast that for each particle don't remember their partners. As a result, the energy transferred in every collision between two particles are no longer correlated, which is equivalent to say that two-particle analysis breaks down. Instead, the energy transfer is completely random, with a non-zero amplitude. On the single-particle energy diagram, what we expected to see is a ``one dimensional random walk" ,so energy levels quickly spread around the diagram.

@@

But intuitively, one will expect that if we measure the energy of a subsystem, e.g. one particle, then we will get a Boltzmann distribution because the rest part of the system serves as a bath for this particle. The temperature of this isolated system is defined according to $Nk_BT=E$. It is evident that this argument only hold when the energy of the single particle is not too big --- if one particle take up 50\% of the total energy, the rest could no longer be thought of as a good bath.
